My title

### 2023-03-15 outputs/paper/Happiness in America: A Comprehensive Analysis of the Effects of Demographic Factors.qmd
readme file editted

ggplot(happiness_data, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = happy_colors) +
  scale_color_manual(values = happy_colors) +
  labs(x = "Year", y = "Number of Respondents", fill = "Happy Level", 
       title = "Changes in happiness levels from 1972 to 2021",
       color = "Happy level")

@@

ggplot(sex_data_happy1, aes(x = Year, y = People, fill = Sex)) +
  geom_line(aes(group = Sex, color = Sex), size = 1.2) +
  scale_fill_manual(values = sex_colors) +
  scale_color_manual(values = sex_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Sex", title = "Trends in happiness level (very happy) by gender from 1972 to 2021")

@@

ggplot(sex_data_happy2, aes(x = Year, y = People, fill = Sex)) +
  geom_line(aes(group = Sex, color = Sex), size = 1.2) +
  scale_fill_manual(values = sex_colors) +
  scale_color_manual(values = sex_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Sex", title = "Trends in happiness level (pretty happy) by gender from 1972 to 2021")

@@

ggplot(sex_data_happy3, aes(x = Year, y = People, fill = Sex)) +
  geom_line(aes(group = Sex, color = Sex), size = 1.2) +
  scale_fill_manual(values = sex_colors) +
  scale_color_manual(values = sex_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Sex", title = "Trends in happiness level (not too happy) by gender from 1972 to 2021")

@@

ggplot(race_data_happy1, aes(x = Year, y = People, fill = Race)) +
  geom_line(aes(group = Race, color = Race), size = 1.2) +
  scale_fill_manual(values = race_colors) +
  scale_color_manual(values = race_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Race", title = "Trends in happiness level (very happy) by race from 1972 to 2021")

@@

ggplot(race_data_happy2, aes(x = Year, y = People, fill = Race)) +
  geom_line(aes(group = Race, color = Race), size = 1.2) +
  scale_fill_manual(values = race_colors) +
  scale_color_manual(values = race_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Race", title = "Trends in happiness level (pretty happy) by race from 1972 to 2021")

@@

ggplot(race_data_happy3, aes(x = Year, y = People, fill = Race)) +
  geom_line(aes(group = Race, color = Race), size = 1.2) +
  scale_fill_manual(values = race_colors) +
  scale_color_manual(values = race_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Race", title = "Trends in happiness level (not too happy) by race from 1972 to 2021")

@@

ggplot(degree_data_1, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = degree_colors) +
  scale_color_manual(values = degree_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Happy level", title = "Changes in happiness levels of individuals \nwith less than high school education from 1972 to 2021", color = "Happy level")

@@

ggplot(degree_data_2, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = degree_colors) +
  scale_color_manual(values = degree_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Happy level", title = "Changes in happiness levels of individuals \nwith high school education from 1972 to 2021", color = "Happy level")

```
```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-10AssociateCollege
#| fig-cap: "Changes in happiness levels of individuals with associate/junior college education from 1972 to 2021"

@@

ggplot(degree_data_3, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = degree_colors) +
  scale_color_manual(values = degree_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Happy level", title = "Changes in happiness levels of individuals \nwith associate/junior college education from 1972 to 2021", color = "Happy level")
```

@@

ggplot(degree_data_4, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = degree_colors) +
  scale_color_manual(values = degree_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Happy level", title = "Changes in happiness levels of individuals \nwith bachelor's education from 1972 to 2021", color = "Happy level")

@@

ggplot(degree_data_5, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = degree_colors) +
  scale_color_manual(values = degree_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Happy level", title = "Changes in happiness levels of individuals \nwith graduate education from 1972 to 2021", color = "Happy level")

@@

ggplot(employee_status_data_happy1, aes(x = Year, y = People, fill = Employee_status)) +
  geom_line(aes(group = Employee_status, color = Employee_status), size = 1.2) +
  scale_fill_manual(values = employee_status_colors) +
  scale_color_manual(values = employee_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Employee status", title = "Trends in happiness level (very happy) by employee status from 1972 to 2021", color = "Employee status")

@@

ggplot(employee_status_data_happy2, aes(x = Year, y = People, fill = Employee_status)) +
  geom_line(aes(group = Employee_status, color = Employee_status), size = 1.2) +
  scale_fill_manual(values = employee_status_colors) +
  scale_color_manual(values = employee_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Employee status", title = "Trends in happiness level (pretty happy) by employee status from 1972 to 2021", color = "Employee status")
```

@@

ggplot(employee_status_data_happy3, aes(x = Year, y = People, fill = Employee_status)) +
  geom_line(aes(group = Employee_status, color = Employee_status), size = 1.2) +
  scale_fill_manual(values = employee_status_colors) +
  scale_color_manual(values = employee_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Employee status", title = "Trends in happiness level (not too happy) by employee status from 1972 to 2021", color = "Employee status")
```
```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-16MaritalStatusVeryHappy
#| fig-cap: "Trends in Happiness Level (very happy) by Marital Status from 1972 to 2021"

@@

ggplot(marital_status_data_happy1, aes(x = Year, y = People, fill = Marital_status)) +
  geom_line(aes(group = Marital_status, color = Marital_status), size = 1.2) +
  scale_fill_manual(values = marital_status_colors) +
  scale_color_manual(values = marital_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Marital status", title = "Trends in happiness level (very happy) by marital status from 1972 to 2021", color = "Marital status")
```
```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-17MaritalStatusPrettyHappy
#| fig-cap: "Trends in happiness level (pretty happy) by marital status from 1972 to 2021"

@@

ggplot(marital_status_data_happy2, aes(x = Year, y = People, fill = Marital_status)) +
  geom_line(aes(group = Marital_status, color = Marital_status), size = 1.2) +
  scale_fill_manual(values = marital_status_colors) +
  scale_color_manual(values = marital_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Marital status", title = "Trends in happiness level (pretty happy) by marital status from 1972 to 2021", color = "Marital status")
```

@@

ggplot(marital_status_data_happy3, aes(x = Year, y = People, fill = Marital_status)) +
  geom_line(aes(group = Marital_status, color = Marital_status), size = 1.2) +
  scale_fill_manual(values = marital_status_colors) +
  scale_color_manual(values = marital_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Marital status", title = "Trends in happiness level (not too happy) by marital status from 1972 to 2021", color = "Marital status")
```

>>>>

ggplot(happiness_data, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = happy_colors) +
  scale_color_manual(values = happy_colors) +
  labs(x = "Year", y = "Number of Respondents", fill = "Happy Level", 
       title = "Fig1-Changes in happiness levels from 1972 to 2021",
       color = "Happy level")

@@

ggplot(sex_data_happy1, aes(x = Year, y = People, fill = Sex)) +
  geom_line(aes(group = Sex, color = Sex), size = 1.2) +
  scale_fill_manual(values = sex_colors) +
  scale_color_manual(values = sex_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Sex", title = "Fig2-Trends in happiness level (very happy) by gender from 1972 to 2021")

@@

ggplot(sex_data_happy2, aes(x = Year, y = People, fill = Sex)) +
  geom_line(aes(group = Sex, color = Sex), size = 1.2) +
  scale_fill_manual(values = sex_colors) +
  scale_color_manual(values = sex_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Sex", title = "Fig3-Trends in happiness level (pretty happy) by gender from 1972 to 2021")

@@

ggplot(sex_data_happy3, aes(x = Year, y = People, fill = Sex)) +
  geom_line(aes(group = Sex, color = Sex), size = 1.2) +
  scale_fill_manual(values = sex_colors) +
  scale_color_manual(values = sex_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Sex", title = "Fig4-Trends in happiness level (not too happy) by gender from 1972 to 2021")

@@

ggplot(race_data_happy1, aes(x = Year, y = People, fill = Race)) +
  geom_line(aes(group = Race, color = Race), size = 1.2) +
  scale_fill_manual(values = race_colors) +
  scale_color_manual(values = race_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Race", title = "Fig5-Trends in happiness level (very happy) by race from 1972 to 2021")

@@

ggplot(race_data_happy2, aes(x = Year, y = People, fill = Race)) +
  geom_line(aes(group = Race, color = Race), size = 1.2) +
  scale_fill_manual(values = race_colors) +
  scale_color_manual(values = race_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Race", title = "Fig6-Trends in happiness level (pretty happy) by race from 1972 to 2021")

@@

ggplot(race_data_happy3, aes(x = Year, y = People, fill = Race)) +
  geom_line(aes(group = Race, color = Race), size = 1.2) +
  scale_fill_manual(values = race_colors) +
  scale_color_manual(values = race_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Race", title = "Fig7-Trends in happiness level (not too happy) by race from 1972 to 2021")

@@

ggplot(degree_data_1, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = degree_colors) +
  scale_color_manual(values = degree_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Happy level", title = "Fig8-Changes in happiness levels of individuals \nwith less than high school education from 1972 to 2021", color = "Happy level")

@@

ggplot(degree_data_2, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = degree_colors) +
  scale_color_manual(values = degree_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Happy level", title = "Fig9-Changes in happiness levels of individuals \nwith high school education from 1972 to 2021", color = "Happy level")

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-10AssociateCollege
#| fig-cap: "Changes in happiness levels of individuals with associate/junior college education from 1972 to 2021"

@@

ggplot(degree_data_3, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = degree_colors) +
  scale_color_manual(values = degree_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Happy level", title = "Fig10-Changes in happiness levels of individuals \nwith associate/junior college education from 1972 to 2021", color = "Happy level")
```

@@

ggplot(degree_data_4, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = degree_colors) +
  scale_color_manual(values = degree_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Happy level", title = "Fig11-Changes in happiness levels of individuals \nwith bachelor's education from 1972 to 2021", color = "Happy level")

@@

ggplot(degree_data_5, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = degree_colors) +
  scale_color_manual(values = degree_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Happy level", title = "Fig12-Changes in happiness levels of individuals \nwith graduate education from 1972 to 2021", color = "Happy level")

@@

ggplot(employee_status_data_happy1, aes(x = Year, y = People, fill = Employee_status)) +
  geom_line(aes(group = Employee_status, color = Employee_status), size = 1.2) +
  scale_fill_manual(values = employee_status_colors) +
  scale_color_manual(values = employee_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Employee status", title = "Fig13-Trends in happiness level (very happy) by employee status from 1972 to 2021", color = "Employee status")

@@

ggplot(employee_status_data_happy2, aes(x = Year, y = People, fill = Employee_status)) +
  geom_line(aes(group = Employee_status, color = Employee_status), size = 1.2) +
  scale_fill_manual(values = employee_status_colors) +
  scale_color_manual(values = employee_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Employee status", title = "Fig14-Trends in happiness level (pretty happy) by employee status from 1972 to 2021", color = "Employee status")
```

@@

ggplot(employee_status_data_happy3, aes(x = Year, y = People, fill = Employee_status)) +
  geom_line(aes(group = Employee_status, color = Employee_status), size = 1.2) +
  scale_fill_manual(values = employee_status_colors) +
  scale_color_manual(values = employee_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Employee status", title = "Fig15-Trends in happiness level (not too happy) by employee status from 1972 to 2021", color = "Employee status")
```
```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-16MaritalStatusVeryHappy
#| fig-cap: "Trends in Happiness Level (very happy) by Marital Status from 1972 to 2021"

@@

ggplot(marital_status_data_happy1, aes(x = Year, y = People, fill = Marital_status)) +
  geom_line(aes(group = Marital_status, color = Marital_status), size = 1.2) +
  scale_fill_manual(values = marital_status_colors) +
  scale_color_manual(values = marital_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Marital status", title = "Fig16-Trends in happiness level (very happy) by marital status from 1972 to 2021", color = "Marital status")
```
```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-17MaritalStatusPrettyHappy
#| fig-cap: "Trends in happiness level (pretty happy) by marital status from 1972 to 2021"

@@

ggplot(marital_status_data_happy2, aes(x = Year, y = People, fill = Marital_status)) +
  geom_line(aes(group = Marital_status, color = Marital_status), size = 1.2) +
  scale_fill_manual(values = marital_status_colors) +
  scale_color_manual(values = marital_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Marital status", title = "Fig17-Trends in happiness level (pretty happy) by marital status from 1972 to 2021", color = "Marital status")
```

@@

ggplot(marital_status_data_happy3, aes(x = Year, y = People, fill = Marital_status)) +
  geom_line(aes(group = Marital_status, color = Marital_status), size = 1.2) +
  scale_fill_manual(values = marital_status_colors) +
  scale_color_manual(values = marital_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Marital status", title = "Fig18-Trends in happiness level (not too happy) by marital status from 1972 to 2021", color = "Marital status")
```
